To make a simplified model, there will be looked at the different test parameters, to see if some of these parameters have significantly less influence on the path loss than others of the test parameters.

In the other PL models, either the distance between the antennas or the height of the transmitting and receiving antenna are used or in the case of TRLP \eqref{two_ray_model} both are used. These parameters also influence the PL significantly. When changing the distance from from measurement point to the next measurement point, there is a decrease in PL of 6 dB across all distances point, which is shown in Table \ref{App1}.

\begin{table}[!htbp]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
   & 1m & 2m & 4m & 8m & 15m & 30m\\
\hline
PL & -34.68 & -41.37 & -49.02 & -57.29 & -66.14 & -72.29 \\
\hline
\end{tabular}
\label{App1}
\caption{Hello}
\end{table}



In Table \ref{App2}, the mean PL across all height setups is shown. It is seen that, at lower heights, the PL increases, which shows a dependency on the heights of the antennas.

\begin{table}[!htbp]
\centering
\begin{tabular}{|c|c|c|c|c|}
\hline
Tx Rx & 0.01m & 0.08m & 0.34m & 2.00m \\
\hline
0.01m & -63.71 & -60.70 & -55.37 & -52.37\\
\hline
0.08m & -60.70 & -58.11 & -53.35 & -50,20\\
\hline
0.34m & -55.37 & -53.35 & -48.99 & -47.64\\
\hline
2.00m & -52.37 & -50.20 & -47.64 & -44.41\\
\hline
\end{tabular}
\caption{Hello}
\label{App2}
\end{table}

Compared to these two parameters, the rest of the test parameters (Placement, Antenna type and Polarization) do have a less impact, as all three parameters only have two different setups and the differences between these setups is 2.23, -4.18, 3.32 dB respectively, and there is no significantly tendencies found in the data for these parameters. This is expected for the placement and antenna type parameters, as the antenna type should not effect the PL, and the differences for the placements is found in the reflection, which have been taking into consideration for each placement. The polarization is also taking into consideration with the reflection and the antenna gains.

So for the test parameters, there will only be seen at the distance between the antennas and height of antennas. The other parameters have a much smaller influence and taking into account in other ways, so will not be looked at.
