%\subsection*{Summary}
The most optimal PL model is the GWPL model \eqref{ground_wave} as it can be seen from the  \autoref{model_comparison}, the GWPL model gets the best coverage of $100\%$, as it takes all waves into account, and has a MSE of 35.49. It is however also the most complicated, as it requires to make measurements at the desired locations.\\
Furthermore by looking at \autoref{model_comparison}, it can be seen that by making the simplification of the GWPL, it is now necessary to look at the conditions for the simplified PL models, as their applicability is now restricted.\\
It can be further seen from \autoref{model_comparison}, that the accuracy of the predictions generally decreases for the simplified PL models. But the general reason of the loss of prediction accuracy is due to some weak points of the simplifications made.
 %not only loses the other models applicability, as it is now necessary to calculate the conditions before assessing the PL, but also the inaccuracy of the prediction increases. 
It can be seen from \autoref{model_comparison}, that the MSE for the NSPL is quite large, this is believed to primarily be due to the measurement uncertainty of $\epsilon_{0}$, as mentioned earlier. \\ 
Where ATRPL has the highest valid region of the simplified models, but has a rather high MSE, this is due to its lack of ability to account for the surface wave, as seen from \eqref{two_ray_model}, when the heights goes to zero, so does the power received. \\
It can be seen that FSPL actually predicts quite well inside its valid region, but it is also the model that has second fewest valid points in the measurement campaign, due to the assumption of no multipath. 
%The NSPL is worst off, lacking in both applicability as well as accuracy, the weak point here is primarily the need to measure $z$. 
This leaves all PL models with crucial weak points, in to much complexity or constrains on coverage area. This paper will now propose a model that accounts for some of these weak points. 

%It is also important to note that the three approximated models of the GWPL \eqref{simple_friss}\eqref{two_ray_model}\eqref{surface_wave}, uses some restriction that make it possible to simplify the equation, but still account for the dominant factors of the GWPL model. Although the NSPL model is based on the parameter $z$, which requires the same measurements as $\epsilon_{0}$, only the size of $z$ is necessary and it can therefore be rather easily estimated. 




